\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-11 paper/main.tex
Added citations for fuzzing tools

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning
  libraries~(DLLs), such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of bug-finding techniques to address this
  problem have been proposed, but the lack of a curated set of
  reproducible bugs in DLLs hinders credible evaluation of these
  techniques. We present \tname, a database of curated reproducible
  bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DLL testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DLL libraries, namely, \jax,
  \tf, and \torch.
\end{abstract}

@@

\sloppy Serveral important application domains (e.g., transportation,
medicine, etc.) use AI to optimize some element of their business
process. Deep Learning libraries~(DLLs), such as \jax, \torch{}, and
\tf{}, provide the building blocks for the AI components of these
applications.  Unfortunately, as any piece of software, these
libraries contain bugs. An impressive number of techniques have been
recently proposed to find bugs in these libraries~\Fix{cite 10+
  fuzzing papers here}, however we observe that the evaluation of
these techniques do \emph{not} use a reference set of reproducible
bugs to evaluate their effectiveness. The lack of evaluation standards
is an obstacle to the fair comparison of techniques, hindering
research progress.

This paper presents \tname, a database of curated reproducible bugs to
enable credible evaluation of DLL testing techniques. \tname\ is
equiped with a command-line interface to enable researchers to analyze
and reproduce bug instances.

@@

Our dataset currently consists of \numbugs{} instances of reproducible
bugs representing three popular DLL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of bug
instances based on releases of the library against those based on
nightly builds, and column ``environment'' shows the breakdown of bug
instances that use Python's virtual environment against those that run
on a Docker container.

@@

\section{\tname: Database of Bugs in DLLs}
\subsection{Bug Interface}
\subsection{Test Oracle}
\subsection{Usage and Setup}

@@

\subsection{Evaluating DLL testing techniques}
\subsection{Fault Detection}
\subsection{Program Repair}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning~(DL)
  libraries, such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of bug-finding techniques to address this
  problem have been proposed, but the lack of a curated set of
  reproducible bugs in DL libraries hinders credible evaluation of these
  techniques. We present \tname, a database of curated reproducible
  bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DL library testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DL libraries, namely, \jax,
  \tf, and \torch.
\end{abstract}

@@

\sloppy Serveral important application domains (e.g., transportation,
medicine, etc.) use AI to optimize some element of their business
process. Deep Learning~(DL) libraries, such as \jax, \torch{}, and
\tf{}, provide the building blocks for the AI components of these
applications.  Unfortunately, as any piece of software, these
libraries contain bugs. An impressive number of techniques have been
recently proposed to find bugs in these libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge}, 
however we observe that the evaluation of
these techniques do \emph{not} use a reference set of reproducible
bugs to evaluate their effectiveness. The lack of evaluation standards
is an obstacle to the fair comparison of techniques, hindering
research progress.

This paper presents \tname, a database of curated reproducible bugs to
enable credible evaluation of DL library testing techniques. \tname\ is
equipped with a command-line interface to enable researchers to analyze
and reproduce bug instances.

@@

Our dataset currently consists of \numbugs{} instances of reproducible
bugs representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of bug
instances based on releases of the library against those based on
nightly builds, and column ``environment'' shows the breakdown of bug
instances that use Python's virtual environment against those that run
on a Docker container.

@@

\section{\tname: Database of Bugs in DL libraries}
\subsection{Bug Interface}
\subsection{Test Oracle}
\subsection{Usage and Setup}

@@

\subsection{Evaluating DL library testing techniques}
\subsection{Fault Detection}
\subsection{Program Repair}
